%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arkadeep Ganguli} % Your name  
\address{+91 700 345 1323 \\ Kolkata, West Bengal, India} % Your phone number and email
\address{\href{mailto:arkadeep.ganguli@gmail.com}{arkadeep.ganguli@gmail.com} \\ \href{https://www.linkedin.com/in/arkadeep-ganguli/}{LinkedIn} \\ \href{https://github.com/ArkadeepGanguli}{GitHub} \\ \href{https://leetcode.com/u/ArkadeepGanguli/}{LeetCode} \\ \href{https://www.hackerrank.com/profile/arkadeep_ganguli}{HackerRank}}
\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science \& Technology} \hfill {July 2023 - Present (Expected: 2027)}
\\ 
Institute of Engineering \& Management (IEM), Kolkata \hfill {CGPA: 9.56/10.00}
\\
University of Engineering \& Management (UEM), Kolkata  

{\bf ISC, Class XII} \hfill {April 2022 - March 2023}
\\ 
Ram Mohan Mission High School, Kolkata \hfill {Aggregate: 88\%}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Programming  Language & C++, Java, C, Python\\    
Databases & MySQL\\
Version Control & Git, GitHub\\
Cloud & GCP\\
Automation & n8n
 
\end{tabular}   

\end{rSection}

%-------------------------------------------------------------------------------
%	PROJECTS

\begin{rSection}{PROJECTS}

\begin{rSubsection}{AI-Based Internship Recommendation System (\href{https://github.com/ArkadeepGanguli/Localhost}{GitHub})} {October 2025 - November 2025}{Project as a part of SIH '25}{}

\item Developed an AI-driven internship recommendation engine using hybrid rule-based filtering and Google Gemini to generate accurate, personalized top 9--10 matches.
\item Built a full-stack application with Vite, React, TailwindCSS, and Node.js (Express), reusing shared TypeScript models for scalable and maintainable development.    
\item Implemented intelligent ranking, mobile-responsive UI/UX, and end-to-end workflow optimizations for fast, \\explainable recommendations. 
 
\end{rSubsection}  

%------------------------------------------------

\begin{rSubsection}{Multimodal Phishing Detection System (\href{https://github.com/ArkadeepGanguli/multimodal-phishing-detection-system}{GitHub})}{September 2025 - November 2025}{Minor Project as a part of curriculum}{} 
\item Built a lightweight multimodal phishing detection system combining URL-based features with webpage screenshot analysis using GradientBoostingClassifier and a custom CNN model.
\item Developed a high-accuracy pipeline with optimized preprocessing, feature extraction, and focal-loss–based training to address class imbalance and improve real-world detection performance.
\item Implemented scalable end-to-end workflows including model fusion, dataset handling, evaluation metrics, and a Streamlit-based deployment-ready architecture for seamless demonstration.


\end{rSubsection}

%-------------------------------------------------


\begin{rSubsection}{Email / SMS Spam Classifier (\href{https://github.com/ArkadeepGanguli/Email-SMS_Spam_Classifier}{GitHub})}{March 2025}{Minor Project as a part of curriculum}{}

\item Built an end-to-end Email \& SMS Spam Classification system using Python, Scikit-learn, NLP preprocessing, and TF-IDF for feature extraction.
\item Trained and compared multiple ML models (Naive Bayes, Logistic Regression, SVM, Random Forest) to achieve high accuracy on noisy real-world text data.    
\item Achieved 97.10\% accuracy through rigorous model evaluation and optimization, supported by a clean, modular codebase with reusable preprocessing and pipeline utilities.  

\end{rSubsection} 

\end{rSection} 

\begin{rSection}{Key Achievements} \itemsep -2pt   

\begin{itemize}
 
\item Solved 200+ problems on LeetCode.
\item 5-star in C on HackerRank.

\end{itemize}  

\end{rSection} 

\end{document}
